\section{Operations}

    This section will discuss the operations.
    In this section, $b_n$ will denote the number of nodes in bucket $n$.

    \subsection{Insertion}

        An item is inserted by performing the following steps:
        \begin{itemize}
            \item calculating the hash of the item ($O(1)$)
            \item choosing the bucket $i$ as explained in the previous section
                ($O(1)$)
            \item conditionally performing a resize (assuming amortized $O(1)$)
            \item inserting the item in the AVL tree, using the hash value as
                key (worst case $O(log(b_i))$)
        \end{itemize}
        The overall worst-case complexity is in $O(log(b_i))$.


    \subsection{Search}

        An item may be found by performing the following steps:
        \begin{itemize}
            \item calculating the hash of the item ($O(1)$)
            \item choosing the bucket $i$ as explained in the previous section
                ($O(1)$)
            \item finding the item in the AVL tree, using the hash value as
                key (worst case $O(log(b_i))$)
        \end{itemize}
        The overall worst-case complexity is in $O(log(b_i))$.


    \subsection{Union}

        The union of two sets is calculated by merging one of the sets into the
        other.
        This is done bucket by bucket.
        If the number of buckets of the operand is lower than the number of
        bucket in the target set, one bucket $i$ is merged by:
        \begin{itemize}
            \item extracting the sub-AVL from the source bucket $s$ (worst case
                $O(log(b_s))$)
            \item merging the extracted sub-AVL into the target bucket
                (worst case $O(b_i+b_s)$)
            \item rebalancing the tree (worst case $O(b_i+b_s)$)
        \end{itemize}

        If, however, the number of buckets the source set consists of is greater
        or equal the number of buckets in the target set, one bucket $i$ is
        merged by performing the following steps:
        \begin{itemize}
             \item merging each source bucket $s$ into the target bucket (worst
                case $O(O(b_i \sum_s b_s))$)
            \item rebalancing the tree (worst case $O(b_i \sum_s b_s)$)
        \end{itemize}

        After the buckets are merged, the hash-table might be resized.

        Although the overall worst case may be $O(in_d+n_s)$, the actual
        operation is expected to be much faster, if some constraints are met.


    \subsection{Intersection}

        The intersection of two sets is calculated by removing elements from a
        target set which are not in a source set.
        This is done bucket by bucket for each of the target set's buckets or,
        if the operand's number of bucket is greater, to each sub-domain
        corresponding to a bucket of the operand.
        %TODO: ref to the algo
        The hash-table might be resized afterwards.


    \subsection{Exclusion}

        The exclusion of elements from a set is done the same way an
        intersection is performed, but negating the predicate for removal of
        elements.
        Exclusion is performed by removing elements which \emph{are} in the
        source set.



